%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Revision By: Athena Liu
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
%\usepackage[pdftex,hidelinks]{hyperref}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{xcolor}


\usepackage[slantfont,boldfont]{xeCJK}
\usepackage{fontspec}
\setCJKmainfont{SimSun}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
\item\small{
\textbf{#1}{: #2 \vspace{-2pt}}
}
}

\newcommand{\resumeItemNoGroup}[1]{
\item\small{
{#1 \vspace{1pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%% CV STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\Large Athena (Xiaohe) LIU}} & \href{https://athenaliu.space/}{\faHome\space athenaliu.space/} \\
\href{https://github.com/XiaoheLiu}{\faGithub\space github.com/XiaoheLiu} & \href{mailto:sdathenaliu@gmail.com}{\faEnvelope\space sdathenaliu@gmail.com}
 \\
\href{https://linkedin.com/in/athenaliuxh/}{\faLinkedin\space linkedin.com/in/athenaliuxh} &
\faMobilePhone\space (+1) 778-554-2230 \\
\end{tabular*}

%--------SUMMARY------------
% \section{Summary}
% \resumeSubHeadingListStart
% \resumeItemNoGroup
% {Ph. D. student in Engineering, seeking internship and full time opportunities in full stack development. }
% \resumeItemNoGroup
% {Focused web developer with confidence in frontend development with ReactJS and backend development with Django (python) and NodeJS.  }
% \resumeItemNoGroup
% {Independent, self-motivated, always eager to learn and implement new technologies to make life better.}
% \resumeItemNoGroup
% {Experience working in team environment and coordinating tasks among team members.}
% \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{University of British Columbia}{Vancouver, BC}
{Ph.D. in Mechanical Engineering - Computational Fluid Mechanics}{Sept 2017 - Present}

\resumeSubheading
{Brown University}{Providence, RI, U.S.A.}
{Ma.Sc. in Engineering}{Sept 2015 - May 2017}
\resumeItemListStart
\resumeItemNoGroup
{\textbf{Courses:} Numerical Solution of Partial Differential Equations, Scientific Programming in C++}
\resumeItemListEnd

\resumeSubheading
{Fudan University}{Shanghai, China}
{Ba.Sc. in Theoretical and Applied Mechanics}{Sept 2011 - July 2015}

\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\resumeSubItem{Programming Languages}
{ Python, C++, JavaScript, GraphQL, SQL, HTML, CSS}
\resumeSubItem{Frameworks}
{ ReactJS,   GatsbyJS, NextJS, Apollo-client, Redux, Jest, Enzyme, NodeJS, Django }
\resumeSubItem{Databases}
{  PostgreSQL, MySQL, MongoDB}
\resumeSubItem{Others}
{ Git, MATLAB, Bash, \LaTeX}
\resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Technical Projects}
\resumeSubHeadingListStart


\resumeSubheading
{SwordRama - Sword Recommender \& Reviews}{}
{Django \& Machine Learning Project}{April 2019}
\resumeItemListStart
\resumeItemNoGroup
{Built a review platform and a recommendation system to share information and get insights on HEMA (Historical European Martial Arts) training swords.}
\resumeItemNoGroup
{Created a sword database based on web resources, and developed filtering and searching functionalities for swords in the web app.}
\resumeItemNoGroup
{Provided customized recommendations for users using K-means clustering as a machine learning algorithm with Pandas, SciPy, Numpy and Scikit-learn.}
\resumeItemNoGroup
{Deployed to production on Heroku (\href{https://swordrama.herokuapp.com}{swordrama.herokuapp.com}).}
\resumeItemListEnd


\resumeSubheading
{Handcrafty - Sell \& Shop for Handmade Items}{}
{React \& GraphQL Project}{Feb - Apr 2019}
\resumeItemListStart
\resumeItemNoGroup
{Built a full-stack Etsy-like web app where user can search, sell, edit, add to cart and buy their favorite handmade products.}
\resumeItemNoGroup
{Created a server side rendered frontend with NextJS, and used Apollo-client for fetching/caching data from the GraphQL backend and local state management; Tested the major components using Jest and Enzyme.}
\resumeItemNoGroup
{Designed extensive relational data models including users, items, orders, shopping cart items, and order items; Implemented the data layer on the backend using GraphQL Yoga and Prisma.}
\resumeItemNoGroup
{Developed server side functionalities including JWT authentication, permissions, email password updates, uploading images, and charging credit cards with StripeJS.}
\resumeItemListEnd

\clearpage

\resumeSubheading
{百字本 (100-Letter) Baizi Journal App}{} 
{React \& Node Project}{Jan - Feb 2019}
\resumeItemListStart
\resumeItemNoGroup
{Designed and developed a minimalist journal app which prompts user to write a journal with 100 Chinese characters exact every day.}
\resumeItemNoGroup
{Reached out to a senior developer and collaborated on backend development, built a REST API with NodeJS, ExpressJS and MongoDB.} 
\resumeItemNoGroup
{Independently developed the frontend with React and Redux, implemented routing using React Router, and integrated with the backend using Axios and Redux Thunk.}
\resumeItemListEnd

\resumeSubheading
{Computational Modeling of High Speed Jet Impingement}{}
{Research Project}{June - Oct 2018}
\resumeItemListStart
\resumeItemNoGroup
{Developed numerical procedures in C using an open source software named {\emph{Basilisk}}, to simulate high speed liquid jet impingement on a moving surface, providing physical insight to the phenomena that was not observable through experiments.}
\resumeItemNoGroup
{Used supercomputing and MPI parallel algorithm to accelerate the computation, reducing the runtime by 99\%. }
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Lead Teaching Assistant (Statistics \& Machine Learning)}{Vancouver, BC}
{Department of Mechanical Engineering, UBC}{Jan 2018 - Present}
\resumeItemListStart
\resumeItemNoGroup
{Create and teach tutorials for 3rd year undergraduate students on statistics and machine learning. Tutorials include hands-on data analysis with MATLAB and python, and white board explanation on mathematical concepts and textbook problems. } 
\resumeItemNoGroup
{Coordinate with 2 professors and 7 other TAs throughout the term to ensure that the tutorial materials are complementary to the rest of the course. Deliver 6 hours of lectures to a class of 20-50 people every other week for 10 weeks.}
\resumeItemNoGroup
{First taught this tutorial in 2018 and was invited to teach again as lead TA in 2019 thanks to the good feedbacks from the students and instructors. }
\resumeItemListEnd

\resumeSubheading
{Administrative Intern}{Shanghai, China}
{InnoSpace Startup Incubator}{March - June 2015}
\resumeItemListStart
\resumeItemNoGroup
{Coordinated among 20+ onsite web-oriented startup teams, the administrative staff and external investors, to ensure projects stayed on schedule and stakeholders were informed of project status.}  
\resumeItemNoGroup
{Provided administrative support including front-desk reception, schedule management, event planning and social media marketing.}  
\resumeItemListEnd

\resumeSubHeadingListEnd


%--------INTERESTS------------
\section{Other Skills \& Interests}
\resumeSubHeadingListStart
\resumeSubItem{Languages }{English (Fluent), Mandarin (Native), French (Conversational), Japanese (Basic)}
\resumeSubItem{Interests}{Historical Rapier Fencing, Origami, Stamp Carving}
\resumeSubHeadingListEnd


%----------Footer-----------------
\vspace*{\fill}
\color{gray}
\small
%\titlerule\vspace{5pt}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Athena (Xiaohe) LIU}} & \href{https://athenaliu.space/}{\faHome\space athenaliu.space/} \\
\href{https://github.com/XiaoheLiu}{\faGithub\space github.com/XiaoheLiu} & \href{mailto:sdathenaliu@gmail.com}{\faEnvelope\space sdathenaliu@gmail.com}
 \\
\href{https://linkedin.com/in/athenaliuxh/}{\faLinkedin\space linkedin.com/in/athenaliuxh} &
\faMobilePhone\space (+1) 778-554-2230 \\
\end{tabular*}
%-------------------------------------------
\end{document}
